\documentclass[12pt,a4paper]{article}
\usepackage[a4paper,margin=3cm]{geometry}

\input{preamble}

% Decrease/control white space above title
\usepackage{titling}
\setlength{\droptitle}{-2cm}

%% Date settings for \today
\usepackage{datetime}
% Declare a new date format
\newdateformat{monthyear}{\monthname[\THEMONTH] \THEYEAR}
% Indicate that we should actually _use_ this format for \today
\monthyear

\title{\bfseries \huge Rob Cornish}
% XXX: Really should be \subtitle, but no easy way to do this..
\author{Curriculum Vitae}
\date{\today}

\begin{document}
\maketitle
\nobibliography{main}
\bibliographystyle{unsrt}

% Suppress page numbering on first page
\thispagestyle{empty}
% Control space between title and first section
%%\vspace{3em}

%\section*{Contact details}
\begin{llist}
  \textit{Full name} & John Robert Macaulay Cornish \\
  \textit{Address} & 13 Vicarage Road, Oxford, OX14RB, United Kingdom\\
  \textit{Date of Birth} & 23rd January, 1992 \\
  \textit{Telephone} & +44 7908 000 873 \\
  \textit{Email} & \mailto{rcornish@robots.ox.ac.uk}
\end{llist}

\section*{Education}

\begin{llist}
  2015-present & CDT DPhil in Autonomous Intelligent Machines and Systems, University of
  Oxford. \textit{Supervisors:} Arnaud Doucet and George Deligiannidis. \\
  2014-2015 & Bachelor of Science (Honours) in Mathematics and Statistics, Monash University,
  majoring in Applied Mathematics. GPA: 4.0/4.0 (First Class Honours) \\ 
  2012-2014 & Bachelor of Science, University of Melbourne, majoring in
  Electrical Systems. GPA: 86/100 (First Class Honours) \\
  2011-2014 & Diploma of Mathematical Sciences, University of Melbourne,
  majoring in Pure Mathematics. GPA: 88/100 (First Class Honours) \\
  2010-2012 & Bachelor of Arts, University of Melbourne, majoring in Philosophy
  and History and Philosophy of Science. (Transferred to BSc in 2012.) \\
  2009 & VCE ENTER (tertiary entrance for Victoria, Australia) percentile ranking of 99.55
\end{llist}

\section*{Experience}
\begin{llist}
  2018-present & Co-founder \& CTO, Quro Medical -- a South African digital health startup pioneering premium hospital-at-home services in Southern Africa. \url{www.quromedical.co.za} \\
  2014-2015 & Mathematics tutor, Monash University \\
  2014-2015 & Monash University Honours research project. \textit{Topic:}
  Detection and Tracking of Surface Primitives in RGBD Data. \textit{Supervisors:}
    Prof. Tom Drummond, Dr. Norman Do. \\
  2013-2014 (summer) & Research assistant at CSIRO's Queensland Center
    for Advanced Technologies (QCAT). \textit{Topic:} robotic deployment of the HeatWave
    thermography device. \textit{Supervisor:} Dr. Peyman Moghadam. \\
  2012-2014 & Research assistant with Optimization and Programming Languages Research
    Group at The University of Melbourne. \textit{Topic:} analysis and verification of
    array manipulating programs.  \textit{Supervisor:} A/Prof. Harald S\o ndergaard.
\end{llist}

\section*{Academic publications}

Copies of each of the following papers can be found at \\
\url{http://www.robots.ox.ac.uk/\textasciitilde rcornish/}.

\subsection*{Preprint}

\textbf{Localised Generative Flows} \\
\underline{Rob Cornish}, Anthony L. Caterini, George Deligiannidis, Arnaud Doucet \\
\textit{arXiv preprint arXiv:1909.13833}

\subsection*{Conference}

\textbf{Scalable Metropolis-Hastings for Exact Bayesian Inference with Large Datasets} \\
\underline{Rob Cornish}, Paul Vanetti, Alexandre Bouchard-C\^ot\'e, George Deligiannidis, Arnaud Doucet \\
\textit{International Conference on Machine Learning (ICML), 2019}

\noindent
\textbf{Online Learning Rate Adaptation with Hypergradient Descent} \\
At\i l\i m G\"une\c s Baydin, \underline{Rob Cornish}, David Rubio, Mark Schmidt, Frank Wood \\
\textit{International Conference on Learning Representations (ICLR), 2018}

\noindent
\textbf{On Nesting Monte Carlo Estimators} \\
Tom Rainforth, \underline{Rob Cornish}, Hongseok Yang, Andrew Warrington, Frank Wood \\
\textit{International Conference on Machine Learning (ICML), 2018}

\noindent
\textbf{Analyzing Array Manipulating Programs by Program Transformation} \\
\underline{Rob Cornish}, Graeme Gange, Jorge Navas, Peter Schachte, Harald S\o ndergaard, Peter Stuckey \\
\textit{Logic-Based Program Synthesis and Transformation: Proceedings of the 24th International Symposium, 2015}


\subsection*{Workshop}

\textbf{Robust Out-of-Sample Uncertainty for Neural Networks via Confidence Densities} \\
\underline{Rob Cornish}, George Deligiannidis, Arnaud Doucet \\
\textit{ICML workshop on Uncertainty and Robustness in Deep Learning, 2019}

\noindent
\textbf{Towards a testable notion of generalisation for generative adversarial networks} \\
\underline{Rob Cornish}, Frank Wood, Honseok Yang \\
\textit{NIPS workshop on Deep Learning: Bridging Theory and Practice, 2017}

\noindent
\textbf{Efficient exact inference in discrete Anglican programs} \\
\underline{Rob Cornish}, Frank Wood, Hongseok Yang \\
\textit{POPL workshop on Probabilistic Programming Semantics (PPS), 2017}

\noindent
\textbf{On the Pitfalls of Nested Monte Carlo} \\
Tom Rainforth, \underline{Rob Cornish}, Hongseok Yang, Frank Wood \\
\textit{NIPS Workshop on Advances in Approximate Bayesian Inference, 2016}

\section*{Awards and achievements}

\begin{llist}
  2016 & Carl Moppert Prize in Mathematics from the School of Mathematical Sciences at
         Monash University for ``best overall honours student in the school'' \\
  2015 & Awarded travel grant to attend AMSI Summer School in the Mathematical
         Sciences, University of Newcastle, NSW for January 2015. \\
  2014 & Monash Mathematical Sciences Honours Scholarship \newline \newline
         John Monash Exhibition Prize from the University of Melbourne for ``best overall
         performance in third-year undergraduate Electrical Engineering subjects'' \\
  2013 & Selected for CSIRO (QLD) Computational Infomatics Vacation Scholarship
         program \textit{(Accepted)} \newline \newline
         Selected for CSIRO (NSW) Astronomy and Space Science Vacation
         Scholarship program \textit{(Declined)}\newline \newline
         Selected for the Melbourne University Department of Mathematics and
         Statistics' Vacation Scholarship program \textit{(Declined)} \newline \newline
         Winner of Melbourne University Electrical Engineering Club (MUEEC)
         SumoRobo Competition \\
  2012 & Faculty of Arts Dean's Honours List for 2011 \newline \newline
         Selected for the Melbourne School of Engineering's Summer Research
         Experience program \textit{(Accepted)} \newline \newline
         Selected for the Melbourne University Department of Mathematics and
         Statistics' Vacation Scholarship program \textit{(Declined)} \\
  2011 & Hastie Exhibition from the University of Melbourne for ``highest overall results in two
         Philosophy subjects''
\end{llist}

\section*{Technical Skills}
I am proficient in the following:
\begin{itemize}
  \item Programming languages:
  \begin{itemize}
    \item \textit{Strong:} Python, C/\CPP, Ruby, Javascript, Bash
    \item \textit{Working knowledge:} MATLAB, R, Clojure/Lisp, PHP, Perl
  \end{itemize}
  \item Machine learning frameworks, especially Pytorch, Tensorflow, Scikit-learn
  \item Cloud computing, especially Amazon Web Services
  \item Probabilistic programming systems, especially Anglican
  \item {\LaTeX}
  \item Linux/Unix environment
  \item Version control tools, especially Git and Subversion
  \item Robot Operating System (ROS)
  \item LLVM Compiler Infrastructure Project
\end{itemize}

\end{document}
